### 2024-08-14 data-visualization.qmd
20240814 - color scheme

The R Graph Gallery provides examples of various types of plots: <https://r-graph-gallery.com>.

A key principle of graphic design and data visualization is the importance of contrast.
Each visual component (e.g., line) that is important to see should be easy to distinguish.
For instance, you can highlight lines or points of interest to draw people's attention to the target of interest.
For examples of highlighting in figures, see Figures [-@fig-lineChartHighlighting] (@sec-lineChartHighlighting) and [-@fig-simulationOf10CoinFlips].

@@

@@

>>>>

The R Graph Gallery provides examples of various types of plots: <https://r-graph-gallery.com>.
In this chapter, we will examine how to create statistical graphics to visualize data.
We will create the plots using the `ggplot2` package.
When creating plots in `ggplot2` with multiple points or lines (e.g., multiple players or levels of a predictor variable), it is easiest to do so with the data in [long form](#sec-wideToLong) (as opposed to [wide form](#sec-longToWide)).

A key principle of graphic design and data visualization is the importance of contrast.
Each visual component (e.g., line) that is important to see should be easy to distinguish.
For instance, you can highlight lines or points of interest to draw people's attention to the target of interest.
For examples of highlighting in figures, see Figures [-@fig-lineChartHighlighting] (@sec-lineChartHighlighting) and [-@fig-simulationOf10CoinFlips].
It is also important to use color schemes with distinguishable colors.
Good color schemes for sequential, diverging, and qualitative (i.e., categorical) data are provided by ColorBrewer (<https://colorbrewer2.org>) and are available using the `scale_color_brewer()` and `scale_fill_brewer()` functions of the `ggplot2` package, as demonstrated in @fig-barPlotConfidenceInterval (@sec-barPlotModifiedColorScheme).

@@

### With Error Bars {#sec-barPlotErrorBars}

@@

### Modified Color Scheme {#sec-barPlotModifiedColorScheme}

We can also modify the color scheme, as in @fig-barPlotConfidenceInterval.

ggplot2::ggplot(
  data = player_stats_seasonal_offense_summary %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = position_group,
    y = mean,
    fill = position_group,
    color = position_group
    )
) +
  geom_bar(
    stat = "identity") +
  scale_fill_brewer(palette = "Set1") +
  geom_errorbar(
    aes(
      ymin = ci_lower,
      ymax = ci_upper),
    width = 0.2,
    color = "black"
  ) +
  labs(
    x = "Position",
    y = "Fantasy Points",
    title = "Bar Plot of Fantasy Points by Position"
  ) +
  theme_classic() + 
  theme(legend.position = "none")
```
